Parallel all papers PLS for corn data

### 2019-07-10 MSc Project/Parallel all papers PLS for corn data.Rmd
papers

##2~mp6

@@

>>>>

##2~mp6 0.107

@@

##3~mp6 0.150

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```

##4~mp6 0.370

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(60,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  #boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  #boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)
```
